%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Consultant, Product Manager} % Job title
    {Sii Polska} % Organization
    {Poznań,Poland} % Location
    {Aug. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Product Owner for Master Data as a Service solutions - Prometheus Group}
        \item {Since September 2024 building from scratch platform for document indexing and equipment classification with AI capabilities, \\processing monthly 1M+ documents and 100k+ equipment items.}
        \item {Product Owner working with ~20 engineers on Umetrics Studio platform - Sartorius AG} 
        \item {Delivered several significant upgrades to the platform, such as API capabilities, collaboration features, etc.}
        \item {Tools: Jira, Miro, Confluence, AWS, GitLab}
        \item {Project technologies: C\#, React, Java, Kubernetes}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Product Owner} % Job title
    {Codenotary} % Organization
    {Remote} % Location
    {May 2022 - July 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Guided delivery of all Codenotary's IT products, such as vault.immudb.io, sbomcenter.io, Trustcenter, and Opvizor.}
        \item {Interviewed customers to build and prioritize the product backlog.}
        \item {Collaborated with the engineering manager and global multicultural team to translate market \\and product requirements into documentation, user stories, and test cases.}
        \item {Coordinated refinements, conducted team retrospectives, and implemented engineering best practices.}
        \item {Assisted with release planning and manual testing.}
        \item {Tools: VSCode, Autorest API, GitHub, Miro, MobaXterm}
        \item {Project technologies: Go, Vue, Python, Kubernetes, Docker}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Scrum Product Owner} % Job title
    {Santander Bank Polska} % Organization
    {Poznań, Poland} % Location
    {Feb. 2019 - Apr. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Boosted retail credit sales in digital channels by 20\% with initiatives such as omnichannel lending, individual capacity assessment, \\optimizing user workflows and integrating real-time analytics tools.}
        \item {Implemented KNF recommendations through use case definition, business analysis and team building.}
        \item {Successful cooperation in an intra-bank group on implementation of emergency anti-Covid measures.}
        \item {Drove 15\% increase in customer retention by leading customer feedback integration into product roadmaps, \\reducing feature delivery time by 25\% via Jira automation.}
        \item {Project technologies: Java, OpenShift, AbInitio, Teradata, Python, Jira, Confluence, Miro}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PM / Agile Product Owner} % Job title
    {BZWBK} % Organization
    {Wrocław, Poland} % Location
    {Dec. 2015 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Streamlined project portfolio management for Risk Division, reducing delivery timelines by 25\% through Agile prioritization frameworks.}
        \item {Drove enhancements to the Customer Analytical Repository, providing data for CRM and Risk and increasing current data availability by 300\%.}
        \item {Directed team of 15 data analysts and developers during Santander-Deutsche Bank merger, achieving 100\% uptime and significant NPL reduction.}        
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Specialist -> Manager} % Job title
    {BZWBK} % Organization
    {Poznań, Poland} % Location
    {Aug. 2005 - Jan. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Held various roles in reporting and decision systems development, advancing to a management position in 2009.}
        \item {Oversaw current validation of Credit Risk scorecards, reporting to the Bank's Credit Policy Forum} 
        \item {Test Leader for Risk Division during the merger with Kredyt Bank.}
        \item {Reduced operational costs by 20\% by leading migration of Bank's Decision Engine from Strata CGI to AbInitio, which enhanced processing speed by 300\%.}
        \item {Conducted business analysis, communicated requirements to Java developers.}        
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
